Scikit-learn: API design for machine learning

### 2013-06-20 paper.tex
wordings (3.3, 3.4)

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel will accept a $\gamma$ parameter,
but ignore it, so the grid search would waste time
trying out effectively equivalent parameter settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

@@

In other places of the library, in particular in the vectorization code
for unstructured inputs, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code.
Again, such external user code can be kept agnostic of the \sklearn
class hierarchy.
Communication proceeds by passing object of standard Python/NumPy types.

>>>>

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel could accept a $\gamma$ parameter,
but would ignore it and thus waste computing time trying out effectively
equivalent settings if a single hyper-parameter grid was used insteead.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

@@

In other places of the library, in particular in the vectorization code
for unstructured inputs, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code to obtain the desired behavior.
Again, such external user code can be kept agnostic of the \sklearn
class hierarchy.
Communication proceeds by passing object of standard Python/NumPy types.
